FraCaS: 80 percent complete

### 2019-02-26 paper2018/paper.tex
paper
fix cite

\begin{abstract}
  TODO
\end{abstract}
\section{Introduction}
Natural Language Inference (NLI) is the task of determining of whether
an NL hypothesis H follows from an NL premise(s) P. NLI has received a
lot of attention in the Computational Semantics literature and has
been approached using a variety of techniques, ranging from logical
approaches
\citep{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017},
all the way to the recent Deep Learning (DL) models for NLI. The
latter approaches, following a general trend in NLP, have been
dominating NLI and a number of impressive results have been
produced \citep{kim:2018,radford:2018,liu:2019}.\footnote{These are
  the three systems with the best results on SNLI in increasing
  order at the time of writing.}  State-of-the-art DL systems achieve an accuracy of around
0.9 when tested on suitable datasets. However, the datasets that are
used are assuming a definition of inference that can be thought to be
`looser' or less precise compared to the definition assumed in
platforms based in logical approaches. Consider the following
two examples, one from the SNLI dataset, predominatly used to test DL
approaches and which has a state-of-the-art performace of 0.911
\citet{lui:2019'}, and the FraCaS test suite, the dataset \textit{par
  excellence} to test logical approaches.
%
The following two examples illustrate the issue.
\begin{lingex}
\item % An SNLI example \\
\textbf{P}  A  man selling donuts to a customer during a world
exhibition event held in the city of Angeles. \\
 \textbf{H}  A woman drinks her coffee in a small cafe.\\
\textbf{Label: Contradiction} [SNLI]
\item % An example from FraCaS\\
\textbf{P1}] A Scandinavian won the Nobel Prize.\\
\textbf{P2}	Every Swede is  Scandinavian.\\
\textbf{Q}  Did a Swede win the Nobel prize? \\
\textbf{H} A Swede won the Nobel prize.\\
\textbf{Label: Yes} [FraCaS 173]
\end{lingex}
%
In the SNLI example, one has to make a number of non-trivial
assumptions in order to arrive at a contradiction: a) the two
situations described have to be taken to refer to the same situation
and, thus, decide whether one description contradicts the other, b)
the indefinite article in the premise has to be identified with the
indefinite article in the hypothesis. (Additionally considering that a
person cannot be a man selling donuts and a woman drinking coffee at
the same time.) While this can be part of the reasoning humans
perform, it is not the only possibility. More precise, logical
reasoning can be also performed. Such an example is the FraCaS
example, as well as very fine-grained cases like the Antecedent
Contained Deletion ellipsis example below:

@@

For this reason, and despite the dominance of DL approaches in pretty
much all NLP tasks, logical approaches continue to be
developed and evaluated on datasets like the FraCaS test suite and the
SICK dataset \cite{marelli:2014}.  \citet{bernardy:2017} define a
correspondence between abstract syntax parse trees of the FraCas
examples, parsed using the Grammatical Framework (GF,
\citet{Ranta:GF}), and modern type-theoretic semantics that are output
in the Coq proof assistant (the FraCoq system).  The accuracy is 0.85
for 5 sections of the FraCaS test suite. The \textsc{Langpro} system
presented by \citet{abzianidze:2017} is based on a Natural Logic
tableau theorem prover. It achieves an accuracy of .82 on the SICK
dataset.

@@

\paragraph{Adjectives}
In our system, we interpret gradable adjectives using a pair of a
measure $m : objects → Z$ and and a threshold $τ : Z$, where $Z$ is
treated as an abstract ordered ring by Coq. (This structure has no
dynamic aspect in our model, and thus is entirely handled within Coq.)
For subsective adjectives, $τ$ will additionally depend on the class
of the object in question. This structure has the benefit that
opposite adjectives can be easily represented (measures are opposites
$∀x. m_1 x = -m_2 x$ and thresholds do not overlap $τ_1 + τ_2 >
0$). Formalization aside, this idea is reminiscent of degree-based
approaches to gradable adjectives of
\citet{Cresswell:1976,Heim:1985,Kennedy:2007}.  Additionally,
adjectival phrases, as present in the FraCaS suite, are interpreted as
linear inequations in $Z$. Solving systems of such inequations is
decidable. Indeed, the tactic that Coq offers for this purpose can
solve all such problems in the FraCaS suite, automatically.

>>>>

\begin{abstract}
  TODO
\end{abstract}
\section{Introduction}
Natural Language Inference (NLI) is the task of determining of whether
an NL hypothesis H follows from an NL premise(s) P. NLI has received a
lot of attention in the Computational Semantics literature and has
been approached using a variety of techniques, ranging from logical
approaches
\citep{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017},
all the way to the recent Deep Learning (DL) models for NLI. The
latter approaches, following a general trend in NLP, have been
dominating NLI and a number of impressive results have been
produced \citep{kim:2018,radford:2018,liu:2019}.\footnote{These are
  the three systems with the best results on SNLI in increasing
  order at the time of writing.}  State-of-the-art DL systems achieve an accuracy of around
0.9 when tested on suitable datasets. However, the datasets that are
used are assuming a definition of inference that can be thought to be
`looser' or less precise compared to the definition assumed in
platforms based in logical approaches. Consider the following
two examples, one from the SNLI dataset, predominatly used to test DL
approaches and which has a state-of-the-art performace of 0.911
\citet{liu:2019}, and the FraCaS test suite, the dataset \textit{par
  excellence} to test logical approaches.
%
The following two examples illustrate the issue.
\begin{lingex}
\item % An SNLI example \\
\textbf{P}  A  man selling donuts to a customer during a world
exhibition event held in the city of Angeles. \\
 \textbf{H}  A woman drinks her coffee in a small cafe.\\
\textbf{Label: Contradiction} [SNLI]
\item % An example from FraCaS\\
\textbf{P1}] A Scandinavian won the Nobel Prize.\\
\textbf{P2}	Every Swede is  Scandinavian.\\
\textbf{Q}  Did a Swede win the Nobel prize? \\
\textbf{H} A Swede won the Nobel prize.\\
\textbf{Label: Yes} [FraCaS 173]
\end{lingex}
%
In the SNLI example, one has to make a number of non-trivial
assumptions in order to arrive at a contradiction: a) the two
situations described have to be taken to refer to the same situation
and, thus, decide whether one description contradicts the other, b)
the indefinite article in the premise has to be identified with the
indefinite article in the hypothesis. (Additionally considering that a
person cannot be a man selling donuts and a woman drinking coffee at
the same time.) While this can be part of the reasoning humans
perform, it is not the only possibility. More precise, logical
reasoning can be also performed. Such an example is the FraCaS
example, as well as very fine-grained cases like the Antecedent
Contained Deletion ellipsis example below:

@@

For this reason, and despite the dominance of DL approaches in pretty
much all NLP tasks, logical approaches continue to be
developed and evaluated on datasets like the FraCaS test suite and the
SICK dataset \cite{marelli:2014}.  \citet{bernardy:2017} define a
correspondence between abstract syntax parse trees of the FraCas
examples, parsed using the Grammatical Framework (GF,
\citet{Ranta:GF}), and modern type-theoretic semantics that are output
in the Coq proof assistant (the FraCoq system).  The accuracy is 0.85
for 5 sections of the FraCaS test suite. The \textsc{Langpro} system
presented by \citet{Abzianidze:2015} is based on a Natural Logic
tableau theorem prover. It achieves an accuracy of .82 on the SICK
dataset.

@@

\paragraph{Adjectives}
In our system, we interpret gradable adjectives using a pair of a
measure $m : objects → Z$ and and a threshold $τ : Z$, where $Z$ is
treated as an abstract ordered ring by Coq. (This structure has no
dynamic aspect in our model, and thus is entirely handled within Coq.)
For subsective adjectives, $τ$ will additionally depend on the class
of the object in question. This structure has the benefit that
opposite adjectives can be easily represented (measures are opposites
$∀x. m_1 x = -m_2 x$ and thresholds do not overlap $τ_1 + τ_2 >
0$). Formalization aside, this idea is reminiscent of degree-based
approaches to gradable adjectives of
\citet{Cresswell:1976,Kennedy:2007}.  Additionally,
adjectival phrases, as present in the FraCaS suite, are interpreted as
linear inequations in $Z$. Solving systems of such inequations is
decidable. Indeed, the tactic that Coq offers for this purpose can
solve all such problems in the FraCaS suite, automatically.
